Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

Overall, the general feeling that transpires from the survey is that it is
essential for any institution to take into account stakeholders' opinions when
introducing chatbots. This is true almost across the board for any new
technology, but in the case of chatbots (and instant messaging applications)
their immediacy and the fact that they can enter into what we could call the
private sphere makes this even more necessary.

>>>>

Overall, the general feeling that transpires from the survey is that it is
essential for any institution to take into account stakeholders' opinions when
introducing chatbots. This is true almost across the board for any new
technology, but in the case of chatbots (and instant messaging applications)
their immediacy and the fact that they can invade what we could call the
private sphere makes this even more necessary.
